---
title:  "Make your own coronavirus plot"
author: "[Matthew Aldridge](https://mpaldridge.github.io)"
date:   "20 June 2020"
output: github_document
---

## Data collection

We can collect the data from [the government's Coronavirus data website](https://coronavirus.data.gov.uk/).

```{r}
govdata <- read.csv("https://coronavirus.data.gov.uk/downloads/csv/coronavirus-deaths_latest.csv")
```

A bit of tidying: the reporting date is in fact a date, and we only want data for the whole of the UK.

```{r}
govdata$Reporting.date <- as.Date(govdata$Reporting.date)

govdata <- subset(govdata, Area.name == "United Kingdom")
```


## Moving average

The data for reported deaths shows a strong "weekend effect", so it makes sense to smooth out the data with a 7-day moving average.

```{r}
MovAv <- function(x, n = 7) as.vector(filter(x, rep(1 / n, n), sides = 2))

govdata$Daily.average <- MovAv(govdata$Daily.change.in.deaths)
```


## Plot a graph

We can now plot a graph of the data.

```{r plot, fig.height = 5.5}
plot(Daily.average ~ Reporting.date, data = govdata,
     main = "Coronavirus daily deaths in the UK",
     ylim = c(10, 1000), log = "y",
     xlab = "Date", ylab = "Daily reported deaths (7-day average)",
     type = "l", col = "blue", lwd = "2")
abline(h = 10^(2:4), col = "grey", lty = 3)
```
